---
title: "regression_tidymodels"
output: html_notebook
---

Another demo of how to do linear regression by group using tidymodels package.  

Source: https://stackoverflow.com/questions/62687664/map-tidymodels-process-to-a-list-group-by-or-nest

Load tidymodels packages
```{r}
#library(broom)
#library(tidyr)
#library(purrr)
library(tidymodels)
```
Example data
```{r}
data("hpc_cv")
glimpse(hpc_cv)
```
Create some data
```{r}
# a df with 504 observations of 4 columns
df <- data.frame(
  hour  = factor(rep(1:24, each = 21)),
  price = runif(504, min = -10, max = 125), #uniform distribution
  wind  = runif(504, min = 0, max = 2500),
  temp  = runif(504, min = -10, max = 25)
)

glimpse(df)
```

Run lm() calls by grouping variable hour using tidymodels.

We can do that by setting up a function to do all the tidymodel fitting and predicting, then use map() through a nested data.frame.

First we define things that we prefer to keep outside the function and then create function.
```{r}

# create model mode and set engine using parsnip
lm_mod <- 
  linear_reg(mode = "regression") %>%
  set_engine("lm")

# create a workflow using workflows
wf <- 
  workflow() %>%
  add_model(lm_mod) # adds a parsnip model to wf


## define big function for model fitting and predicting
predict_price <- function(df) {
  
  split     <- initial_split(df)
  train_df  <- training(split)
  test_df   <- testing(split)
  
  #create recipe
  recipe_train <-
    recipe(price ~ temp + wind, data = train_df) %>%
    step_normalize(all_predictors())
  
  # fit workflow on train data
  fit_wf <-
    wf %>%
    add_recipe(recipe_train) %>%
    fit(data = train_df)
  
  # predict on test data - Do we need this now? We want the coefficients first!
  #predict(fit_wf, test_df)
  
}

```

Now we nest our data

```{r}
df_n <- df %>%
  group_by(hour) %>%
  nest()
```

Then we map() over these nested dataframes with the created function predict_price.

```{r}
system.time(

  res <- df_n %>%
  mutate(predictions = map(data, possibly(predict_price, otherwise = NA)))

)
```
The output res is a dataframe containing:  
1. hour: factor variable with levels 1-24
2. data: list of data frames 21 x 3 (rows x cols)
3. models: list of lists per group 1-24

Ungroup the results
```{r}

res_un <- res %>%
  ungroup %>%
  mutate(HourCoef = map(models, tidy)) %>%
  transmute(hour, modelStats = map(models, glance))

# How does broom work with workflow objects and tidymodels??

# This is what we wnat for each group (hour)
tidy(res[[3]][[1]]$fit$fit$fit)

# ...work on this pipe flow! TBD
res %>%
  ungroup %>%
  mutate(HourCoef = map(predictions, tidy))



# reference below...
res_un <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) %>%
  ungroup() %>%
  mutate(HourCoef = map(fitHour, tidy)) %>%
  transmute(hour, HourCoef, modelStats = map(fitHour, glance)) %>% # Use glance to get the
  unnest(HourCoef, modelStats)
```



