---
title: "regression_broom"
output: html_notebook
---

This is a demo of how to fit lm() regression by group and get the results back using broom.  

Source: https://stackoverflow.com/questions/62972843/retreiving-tidy-results-from-regression-by-group-with-broom

Load libs
```{r}
library(dplyr)
library(broom)
```

```{r}
sessionInfo()
```
Create data for modelling
```{r}
# a df with 504 observations of 4 columns
df <- data.frame(
  hour  = factor(rep(1:24, each = 21)),
  price = runif(504, min = -10, max = 125), #uniform distribution
  wind  = runif(504, min = 0, max = 2500),
  temp  = runif(504, min = -10, max = 25)
)

glimpse(df)
```
Check the data by group hours.
```{r}
df %>%
  group_by(hour) %>%
  summarise(min_price = min(price),
            avg_price = mean(price),
            max_price = max(price),
            .groups = "drop") # this drops the info message from dplyr "ungrouping output.."
```
We see that the min, avg, max values of price varies across the 24 groups.

Run lm() calls by grouping variable hour.
```{r}
library(purrr) #needed for map

# Run lm() per hour as price regressed on wind + temp
res <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) # using dplyr::do

# This creates a data frame object with 24 rows of 
# 1. hour: factor col which is our grouping attribute rowwise with id 1-24
# 2. fitHour: list with one model per group id 1-24 

# We can ungroup ... 

res_1 <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) %>%
  ungroup %>%
  mutate(HourCoef = map(fitHour, tidy)) # we loop over the col 2 list with map and tidy it to a new list column

# This creates a similar dataframe as res one with additional column
# 3. HourCoef: list with tidy model parameters: term, estiate, std.error, stat, pvalue

# ... or we can use unnest after the mutate

res_2 <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) %>%
  ungroup %>%
  transmute(hour, HourCoef = map(fitHour, tidy)) # map to apply tidy on each model

# This creates a similar dataframe as res_1 without the fitHour col, only 1 and 3.

# ...then we do the unnest after the mutate (transmutate) 
library(tidyr)

res_2b <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) %>%
  ungroup %>%
  transmute(hour, HourCoef = map(fitHour, tidy)) %>% # map to apply tidy on each model
  unnest(HourCoef) # Here we unnest the list with coefficients

# This creates df that has one row for each of the three terms (intercept, wind, temp) and their coefficients for every group. 24 x 3 = 72 rows

```

If we want one single data set use pull the firHour and loop over the list with map and condense it to a single dataset by row binding (_dfr suffix)
```{r}
res_2c <- df %>%
  group_by(hour) %>%
  do(fitHour = lm(price ~ wind + temp, data = .)) %>%
  ungroup %>%
  pull(fitHour) %>% # pull all the models
  map_dfr(tidy, .id = "hour") # returns dataframe created by row-binding
```

These results res_2b and res_2c are identical.

